% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chenwei Song}

\basicInfo{
  \email{scw00@apache.com} \textperiodcentered\ 
  \phone{18815655193} \textperiodcentered\ 
  \linkedin[scw00]{https://www.linkedin.com/in/%E8%BE%B0%E4%BC%9F-%E5%AE%8B-83466b142/?locale=en_US}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Tianjin Polytechnic University }, Tianjin, China}{2011 -- 2015}
\textit{B.S.} in Network Engineering 

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
	\item Good at nginx linux development 
    \item Rich experience with development and maintenance in large, distributed scalable systems
	\item Rich experience with developing C/C++/go program 
	\item Rich experience with Linux tool like GDB, systemtap etc.
	\item Good at FreeBSD TCP stack and PMAP 
	\item Apache Traffic Server contributor  
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Iflytek Corp.} Hefei, CN}{Mar. 2017--Present}
\role{Sr. Software Engineer} {}{}
\begin{itemize}
	\item linux maintainance. Solve kernel problems encountered in business scenarios
	\item distributed scalable systems developing. Introducing H2(grpc) technology to update next-generation voice cloud architecture
	\item design and implement Service Orchestration system. Micro-services can be arrangemented in parallel, if-else and sequence by a simple blueprint(JSON)
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Qiniu Corp.} Beijing, CN}{Sept. 2016--2017}
\role{Sr. Software Engineer} {}{}
\begin{itemize}
    \item traffic infrastructure development and maintainance
	\item traffic server slice pluign. Split a large data into small file to accelerate HTTP Range requests
	\item traffic server purge plugin for all file in a directory.
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Letv Corp.} Beijing, CN}{Sept. 2015--2016}
\role{Sr. Software Engineer} {}{}
\begin{itemize}
	\item traffic infrastructure development and maintainance
	\item nginx evelopment and maintainance 
\end{itemize}

\end{document}
